### 2022-12-19 source/paper4.tex
reorganizatin for reproducibility

\begin{figure}[!htb]
\begin{knitrout}
\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}
{\centering \includegraphics[width=\maxwidth]{images/paper4/forest-plot-covid19-1}
}
\end{knitrout}
\caption{Forest plot of fixed-effect meta-analysis of $7$ randomized controlled
  trials investigating association between corticosteroids and mortality in
  hospitalized patients with COVID-19 \citep{REACT2020}. Shown are number of
  deaths among total number of patients for treatment/control group, log odds
  ratio effect estimates with 95\% confidence interval, two-sided $p$-values
  $p$, and prior-predictive tail probabilities $p_{\text{Box}}$ with a
  meta-analytic estimate based on the remaining studies serving as the prior.}
\label{fig4:covid19-meta}
\end{figure}

@@

\section{Reverse-Bayes methods for the assessment of effect estimates}\label{sec4:effects}
A more general question amenable to Reverse-Bayes methods is the assessment of
effect estimates and their statistical significance or non-significance. This
issue has recently attracted intense interest following the public statement of
the American Statistical Association about the misuse and misinterpretation of
the NHST concepts of statistical significance and non-significance
\citep{Wasserstein2016}. First investigated 20 years ago by
\citet{Matthews2001a, Matthews2001b}, Reverse-Bayes methods for assessing both
statistically significant and non-significant findings have been termed the
Analysis of Credibility \citep{Matthews2018} (or AnCred), whose principles and
practice we now briefly review.

@@

Another way to push non-significant findings towards credibility is to use a
prior based on data from another study or a different subgroup. For example,
\citet{Best2021} consider results from the MENSA trial \citep{MENSA2014} on the
efficacy of Mepolizumab against placebo in 551 adult and 25 adolescent patients
with severe asthma. The treatment effect was estimated to be positive in both
subgroups but lacked significance among adolescents. Best et al. combine the
data in the adolescent subgroup with a mixture prior based on a weak and an
informative component. The weak component is a minimally informative normal
prior with mean zero and large variance. The variance is chosen such that the
information content of the prior is equivalent to that provided by a single
subject or event (\emph{unit-information prior}) \citep{Kass1995b}. The other
component is an informative prior based on the (significant) results from the
adolescent subgroup. A Reverse-Bayes approach is used to determine how much
prior weight one needs to assign to the informative component to obtain a
credible posterior result with a 95\% highest posterior credible interval no
longer including zero. In the MENSA trial the required prior weight on the
informative component was 0.7 (and thus 0.3 on the weak prior component) to
achieve a credible result \citep{Best2021}. This illustrates that a considerable
amount of ``Bayesian borrowing'' is required to extrapolate the results from
adults to adolescents.

@@

\citet{Held2019a} refined the concept by suggesting the use of a
prior-predictive check \citep{Box1980, Evans2006} to assess potential prior-data
conflict. With this approach the uncertainty of the estimate $\hat{\theta}$ is
also taken into account since it is based on the prior-predictive distribution,
in this case $\hat\theta \sim \Nor(0, \sigma^2 + \tau^2=\sigma^2 \, (1+g))$ with
$g$ as given in \eqref{eq4:sspv}. Intrinsic credibility is declared if the
(two-sided) tail-probability
\begin{equation*}
  p_{\text{Box}} = \P\left(\chi^2_1 \geq \hat \theta^2/(\sigma^2+\tau^2)\right) = \P\left(\chi^2_1 \geq z^2/(1+g)\right)
\end{equation*}
of $\hat{\theta}$ under the prior-predictive distribution is smaller than
$\alpha$. It turns out that the $p$-value associated with $\theta$ needs to be
at least as small as 0.0056 to obtain intrinsic credibility at level
$\alpha=0.05$, providing another principled argument for the recent proposition
to lower the $p$-value threshold for the claims of new discoveries to 0.005
\citep{Benjamin2017}. A simple check for intrinsic credibility is based on the
\emph{credibility ratio}, the ratio of the upper to the lower limit (or vice
versa) of a confidence interval for a significant effect size estimate. If the
credibility ratio is smaller than 5.8 then the result is intrinsically credible
\citep{Held2019a}. This holds for confidence intervals at all possible values of
$\alpha$, not just for the 0.05 standard. For example, in the RECOVERY study the
95\% confidence interval for the log-odds ratio ranges from $-0.82$ to $-0.25$,
so the credibility ratio is $-0.82/-0.25 = 3.27 < 5.8$ and the result is
intrinsically credible at the standard 5\% level.

@@

Reporting of minimum Bayes factors is one attempt of solving the Problem of
Priors in Bayesian inference. However, this bound may be rather small and the
corresponding prior unrealistic. In contrast, the Reverse-Bayes approach makes
the choice of the prior explicit by determining the relative prior variance
parameter $g$ such that the finding is no longer compelling, followed by
assessing the plausibility of this prior. To do so, one first fixes
$\BF_{01} = \gamma$, where $\gamma$ is a cut-off above which the result is no
longer convincing, for example $\gamma = 1/10$, the level for strong evidence
according to the classification from \citet{Jeffreys1961}. The sufficiently
sceptical relative prior variance is then given by
\begin{align}
\label{ggamma}
  g &=
  \begin{cases}
    -\dfrac{z^2}{q} - 1
    & ~~ \text{if} ~
    -\dfrac{z^2}{q} \geq 1 \\
    \text{undefined} & ~~ \text{else}
  \end{cases} \\
  \text{where} ~ q &=
  \text{W} \left(-\frac{z^2}{\gamma^2} \cdot
  \exp\left\{-z^2\right\}\right)
  \nonumber
\end{align}
where $\text{W}(\cdot)$ is the branch of the Lambert $W$ function that satisfies
$\text{W}(y) \leq -1$ for \mbox{$y \in [-e^{-1}, 0)$} \citep{Corless1996}, see the
Appendix in \citep{Pawel2020b} for a proof.

@@

\section{Bayes factor for intrinsic credibility}
\label{app:BFIC}
Intrinsic credibility at level $\gamma$ is established when
\begin{align}
  \label{eq4:ic-condition}
  \BF_{12} \leq \BF_{01} = \gamma
\end{align}
and we are interested in the Bayes factor for intrinsic credibility $\BFIC$
which is the smallest level $\gamma \in (0, 1]$ where~\eqref{eq4:ic-condition}
holds. The $\BFIC$ is therefore a special case of the sceptical Bayes factor
from \citet{Pawel2020b} where the same data is used in both Bayes factors
(instead of the data from a replication study for $\BF_{12}$). It is hence given
by
\begin{align}
  \label{eq4:BFic}
  \BFIC =
  \begin{cases}
    \sqrt{-z^{2}/k}\cdot \exp\left\{-(z^{2} + k)/2\right\}
    & \text{if} \abs{z} \geq \surd\big\{-2 W\big(-e^{-1}/\sqrt2\big)\big\}\\
    \mbox{minBF}_{01} \
    & \text{if} ~ \sqrt{\log 2} \leq \abs{z} < \surd\big\{-2 W\big(-e^{-1}/\sqrt2\big)\big\} \\
    \text{undefined}
    & \text{if} ~ \abs{z} < \sqrt{\log 2}
  \end{cases}
\end{align}
with $k = W(-z^{2} \exp\{-z^{2}/2\}/\sqrt{2})$ and $W(\cdot)$ the branch of the
Lambert $W$ function that satisfies $W(y) \leq -1$ for $y \in [-e^{-1}, 0).$ If
$\abs{z} \geq \sqrt{-2 W(-e^{-1}/\sqrt2)} \approx 2.04$, $\BFIC$ is located at
the intersection between $\BF_{12}$ and $\BF_{01}$ in the relative prior
variance $g$, so equation (7) from \citet{Pawel2020b} can be used. For
$\abs{z} \geq \sqrt{\log 2} \approx 0.83$, $\BF_{12}$ remains below $\BF_{01}$
for all $g$ and hence $\BFIC$ is given by $\mbox{minBF}_{01}$, the minimum of
$\BF_{01}$ from \eqref{eq4:minBFnorm}. Finally, when $\abs{z} < \sqrt{\log 2}$,
equation~\eqref{eq4:ic-condition} cannot be satisfied for any valid sufficiently
sceptical relative prior variance $g$, hence the $\BFIC$ is undefined.

>>>>

\begin{figure}[!htb]
\begin{knitrout}
\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}
{\centering \includegraphics[width=\maxwidth]{images/paper4/forest-plot-covid19-1}
}
\end{knitrout}
\caption{Forest plot of fixed-effect meta-analysis of $7$ randomized controlled
  trials investigating association between corticosteroids and mortality in
  hospitalized patients with COVID-19 \citep{REACT2020}. Shown are number of
  deaths among total number of patients for treatment/control group, log odds
  ratio effect estimates with 95\% confidence interval, two-sided
  \textit{p}-values $p$, and prior-predictive tail probabilities
  $p_{\text{Box}}$ with a meta-analytic estimate based on the remaining studies
  serving as the prior.}
\label{fig4:covid19-meta}
\end{figure}

@@

\section{Reverse-Bayes methods for the assessment of effect estimates}\label{sec4:effects}
A more general question amenable to Reverse-Bayes methods is the assessment of
effect estimates and their statistical significance or non-significance. This
issue has recently attracted intense interest following the public statement of
the American Statistical Association about the misuse and misinterpretation of
the NHST concepts of statistical significance and non-significance
\citep{Wasserstein2016}. First investigated 20 years ago by
\citet{Matthews2001a, Matthews2001b}, Reverse-Bayes methods for assessing both
statistically significant and non-significant findings have been termed the
Analysis of Credibility, or in short AnCred \citep{Matthews2018}, whose
principles and practice we now briefly review.

@@

Another way to push non-significant findings towards credibility is to use a
prior based on data from another study or a different subgroup. For example,
\citet{Best2021} consider results from the MENSA trial \citep{MENSA2014} on the
efficacy of Mepolizumab against placebo in 551 adult and 25 adolescent patients
with severe asthma. The treatment effect was estimated to be positive in both
subgroups but lacked significance among adolescents. Best et al. combine the
data in the adolescent subgroup with a mixture prior based on a weak and an
informative component. The weak component is a minimally informative normal
prior with mean zero and large variance. The variance is chosen such that the
information content of the prior is equivalent to that provided by a single
subject or event \citep[\emph{unit-information prior},][]{Kass1995b}. The other
component is an informative prior based on the (significant) results from the
adolescent subgroup. A Reverse-Bayes approach is used to determine how much
prior weight one needs to assign to the informative component to obtain a
credible posterior result with a 95\% highest posterior credible interval no
longer including zero. In the MENSA trial the required prior weight on the
informative component was 0.7 (and thus 0.3 on the weak prior component) to
achieve a credible result \citep{Best2021}. This illustrates that a considerable
amount of ``Bayesian borrowing'' is required to extrapolate the results from
adults to adolescents.

@@

\citet{Held2019a} refined the concept by suggesting the use of a
prior-predictive check \citep{Box1980, Evans2006} to assess potential prior-data
conflict. With this approach the uncertainty of the estimate $\hat{\theta}$ is
also taken into account since it is based on the prior-predictive distribution,
in this case $\hat\theta \sim \Nor(0, \sigma^2 + \tau^2=\sigma^2 \, (1+g))$ with
$g$ as given in \eqref{eq4:sspv}. Intrinsic credibility is declared if the
(two-sided) tail-probability
\begin{equation*}
  p_{\text{Box}} = \P\left(\chi^2_1 \geq \hat \theta^2/(\sigma^2+\tau^2)\right) = \P\left(\chi^2_1 \geq z^2/(1+g)\right)
\end{equation*}
of $\hat{\theta}$ under the prior-predictive distribution is smaller than
$\alpha$. It turns out that the $p$-value associated with $\theta$ needs to be
at least as small as 0.0056 to obtain intrinsic credibility at level
$\alpha=0.05$, providing another principled argument for the recent proposition
to lower the \mbox{$p$-value} threshold for the claims of new discoveries to
0.005 \citep{Benjamin2017}. A simple check for intrinsic credibility is based on
the \emph{credibility ratio}, the ratio of the upper to the lower limit (or vice
versa) of a confidence interval for a significant effect size estimate. If the
credibility ratio is smaller than 5.8 then the result is intrinsically credible
\citep{Held2019a}. This holds for confidence intervals at all possible values of
$\alpha$, not just for the 0.05 standard. For example, in the RECOVERY study the
95\% confidence interval for the log-odds ratio ranges from $-0.82$ to $-0.25$,
so the credibility ratio is $-0.82/-0.25 = 3.27 < 5.8$ and the result is
intrinsically credible at the standard 5\% level.

@@

Reporting of minimum Bayes factors is one attempt of solving the Problem of
Priors in Bayesian inference. However, this bound may be rather small and the
corresponding prior unrealistic. In contrast, the Reverse-Bayes approach makes
the choice of the prior explicit by determining the relative prior variance
parameter $g$ such that the finding is no longer compelling, followed by
assessing the plausibility of this prior. To do so, one first fixes
$\BF_{01} = \gamma$, where $\gamma$ is a cut-off above which the result is no
longer convincing, for example $\gamma = 1/10$, the level for strong evidence
according to the classification from \citet{Jeffreys1961}. The sufficiently
sceptical relative prior variance is then given by
\begin{align}
\label{ggamma}
  g &=
  \begin{cases}
    -\dfrac{z^2}{q} - 1
    & ~~ \text{if} ~
    -\dfrac{z^2}{q} \geq 1 \\
    \text{undefined} & ~~ \text{else}
  \end{cases} \\
  \text{where} ~ q &=
  \mathrm{W} \left(-\frac{z^2}{\gamma^2} \cdot
  \exp\left\{-z^2\right\}\right)
  \nonumber
\end{align}
where $\mathrm{W}(\cdot)$ is the branch of the Lambert W function that satisfies
$\mathrm{W}(y) \leq -1$ for \mbox{$y \in [-e^{-1}, 0)$} \citep{Corless1996}, see
the Appendix in \citep{Pawel2020b} for a proof.

@@

\section{Bayes factor for intrinsic credibility}
\label{app:BFIC}
Intrinsic credibility at level $\gamma$ is established when
\begin{align}
  \label{eq4:ic-condition}
  \BF_{12} \leq \BF_{01} = \gamma
\end{align}
and we are interested in the Bayes factor for intrinsic credibility $\BFIC$
which is the smallest level $\gamma \in (0, 1]$ where~\eqref{eq4:ic-condition}
holds. The $\BFIC$ is therefore a special case of the sceptical Bayes factor
from \citet{Pawel2020b} where the same data is used in both Bayes factors
(instead of the data from a replication study for $\BF_{12}$). It is hence given
by
\begin{align}
  \label{eq4:BFic}
  \BFIC =
  \begin{cases}
    \sqrt{-z^{2}/k}\cdot \exp\left\{-(z^{2} + k)/2\right\}
    & \text{if} \abs{z} \geq \surd\big\{-2 W\big(-e^{-1}/\sqrt2\big)\big\}\\
    \mbox{minBF}_{01} \
    & \text{if} ~ \sqrt{\log 2} \leq \abs{z} < \surd\big\{-2 W\big(-e^{-1}/\sqrt2\big)\big\} \\
    \text{undefined}
    & \text{if} ~ \abs{z} < \sqrt{\log 2}
  \end{cases}
\end{align}
with $k = \mathrm{W}(-z^{2} \exp\{-z^{2}/2\}/\sqrt{2})$ and $\mathrm{W}(\cdot)$
the branch of the Lambert W function that satisfies $\mathrm{W}(y) \leq -1$ for
$y \in [-e^{-1}, 0).$ If
$\abs{z} \geq \sqrt{-2 W(-e^{-1}/\sqrt2)} \approx 2.04$, $\BFIC$ is located at
the intersection between $\BF_{12}$ and $\BF_{01}$ in the relative prior
variance $g$, so equation (7) from \citet{Pawel2020b} can be used. For
$\abs{z} \geq \sqrt{\log 2} \approx 0.83$, $\BF_{12}$ remains below $\BF_{01}$
for all $g$ and hence $\BFIC$ is given by $\mbox{minBF}_{01}$, the minimum of
$\BF_{01}$ from \eqref{eq4:minBFnorm}. Finally, when $\abs{z} < \sqrt{\log 2}$,
equation~\eqref{eq4:ic-condition} cannot be satisfied for any valid sufficiently
sceptical relative prior variance $g$, hence the $\BFIC$ is undefined.
